---
title: "Sexual dimorphism in Chinstrap Penguins"
author: "Ahmed Tijani Akinfalabi, University of Potsdam, Germany"
date: "2023-12-12"
---

```{r include=FALSE}
knitr::opts_chunk$set(comment = "###")
```


```{r label=loading,results="hide",echo=FALSE}
library(knitr)
library(palmerpenguins)
library(ggplot2)
```

# Data summary

```{r label=data}
data(penguins)
head(penguins)
df_penguins = data.frame(penguins)

# Used summary to get the overview of the data
summary(df_penguins)

# This table represent the 3 different species and their population on the Island.
table_penguins = table(df_penguins$species, df_penguins$island)
table_penguins

chinstrapData = df_penguins[df_penguins$species == "Chinstrap",]

head(chinstrapData)
nrow(chinstrapData)
```


# Data Visualization

```{r label= GGPLOT}
# Using GGPlot to visualize the difference between Male and Female regarding different attributes

ggplot(chinstrapData, aes(x = sex, y = bill_length_mm)) +
  geom_boxplot() +
  labs(title = "GGPLot of Bill Length against Sex")

ggplot(chinstrapData, aes(x = sex, y = bill_depth_mm)) +
  geom_boxplot() +
  labs(title = "GGPLot of Bill Depth against Sex")

ggplot(chinstrapData, aes(x = sex, y = flipper_length_mm)) +
  geom_boxplot() +
  labs(title = "GGPLot of Flipper Length against Sex")

ggplot(chinstrapData, aes(x = sex, y = body_mass_g)) +
  geom_boxplot() +
  labs(title = "GGPLot of Body mass against Sex")

```


# Tests

# I got different P values in both t tests by just switching the way i Populated the dataframe. INTERESTING! 
```{r label = test}
# Example data frame
chinstrapData_sex_billLength = data.frame(
  Sex = rep(c("Male", "Female"), each = sum(chinstrapData$sex == "male")),
  BillLength = c(chinstrapData$bill_length_mm)
)

head(chinstrapData_sex_billLength)

# Independent samples t-test
t_test_result <- t.test(BillLength ~ Sex, data = chinstrapData_sex_billLength)
print(t_test_result)

```


# T-test sex against bill Length

```{r}
sex = chinstrapData$sex
billLength = chinstrapData$bill_length_mm

df_billL_sex = data.frame(sex , billLength)
df_billL_sex

# Independent samples t-test
t_test_result2 <- t.test(billLength ~ sex, data = df_billL_sex)
print(t_test_result2)

```


# T-test sex against bill depth

```{r}
sex = chinstrapData$sex
billDepth = chinstrapData$bill_depth_mm

df_billD_sex = data.frame(sex , billDepth)
df_billD_sex

# Independent samples t-test
t_test_result3 <- t.test(billDepth ~ sex, data = df_billD_sex)
print(t_test_result3)

```


# T-test sex against flipLength

```{r}
sex = chinstrapData$sex
flipLength = chinstrapData$flipper_length_mm

df_flipL_sex = data.frame(sex , flipLength)
df_flipL_sex

# Independent samples t-test
t_test_result4 <- t.test(flipLength ~ sex, data = df_flipL_sex)
print(t_test_result4)

```


# T-test sex against body mass

```{r}
sex = chinstrapData$sex
body_mass = chinstrapData$body_mass_g

df_body_mass_sex = data.frame(sex , body_mass)
df_body_mass_sex

# Independent samples t-test
t_test_result5 <- t.test(body_mass ~ sex, data = df_body_mass_sex)
print(t_test_result5)

```


# It is worthy to note the differences in p value and t value and to see how great the significant difference.
